---
title: "COVID19_SouthKorea"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
    theme: readable
---

```{r setup, include=FALSE}
library(readr)
library(flexdashboard)
library(shiny)
library(leaflet)
library(dplyr)
library(RColorBrewer)
urlfile= "https://raw.githubusercontent.com/Yunjeong-Kim/covid19_south_korea/master/COVID19_screening_centers.csv"
korean <- read_csv(url(urlfile), locale = locale(date_names = "he", encoding = "UTF-8"))
#define sigungu
korean$sigungu <- as.factor(korean$sigungu)
korean$sido <- as.factor(korean$sido)
singunguname <- levels(korean$sigungu)
sidoname <- levels(korean$sido)
sidoname <- append(sidoname, "All testing centers")
```




Map
=======================================

input {.sidebar}
----------
```{r}
# define inputs
inputPanel( h3('COVID-19 Testing Centers') ) 
inputPanel(h4('Select your area'), selectInput("sido", label = "City or Province", choices = sidoname, selected ="All testing centers", width=180),
selectInput("sigungu", label = "County", choices = singunguname, width=180))
```

<font size="2">Last Updated at</font>
```{r}
inputPanel(h6('03/23/2020'), style = "border-color: #00b4db" ) 
```



output
----------
```{r}
korean <- mutate(korean, centerinformation=paste0('Center Name: ',centername,
                                          '<br>Address: ', address,
                                          '<br>Telephone: ', telephone
                                         )) 
 filtereddata <- reactive({
                if (input$sido== "All testing centers"){
                        korean
                } else{
                        filter(korean, sido == input$sido)%>%
  filter(sigungu %in% input$sigungu)
                }
        })
observeEvent(input$sido,{
        updateSelectInput(
                session,"sigungu", choices = korean$sigungu[korean$sido == input$sido]
        )
})
 
# Draw the map that shows the testing center
pal <- colorFactor(c("#87CEEB", "#ff073a"), domain = c("O", "X"))
icons <- awesomeIcons(
  icon = 'hospital-o',  
  library = 'fa',
    iconColor = ~pal(screentest))
renderLeaflet({leaflet(filtereddata()) %>%
addProviderTiles('Esri.WorldStreetMap', group='Streets') %>%
  addProviderTiles('Esri.WorldImagery',group='Imagery') %>%
  addLayersControl(baseGroups=c('Streets','Imagery'),options = layersControlOptions(collapsed = F, autoZIndex =T)) %>% 
    addCircleMarkers(data= filtereddata(), lng= ~lon, lat= ~lat, color=~pal(screentest))  %>%
    addAwesomeMarkers(lng=~lon, lat=~lat, icon=icons, popup= ~centerinformation) %>% addLegend(pal=pal, values=~screentest, title="Covid-19 test", opacity=1, position="bottomright")
  })

leafletOutput('map', height=0)
```
<font size="1"> Source:[Ministry of Health and Welfare, South Korea](https://www.mohw.go.kr/react/popup_200128_2.html?fbclid=IwAR0naRh5ksc0Vj7HUOboJmf1WLRx2EKV6YnNs_5ns4MJ6YQ2-JzyVwEHNA0)</font>

****
<font size="1">
※ 호흡기 증상이나 코로나19 증상 의심시에는 먼저 관할 보건소 또는 1339콜센터 등의 상담을 받으신 후 선별진료소를 방문하십시오.<br>
※ If you have respiratory symptoms or any sign of possible COVID-19 symptoms, please call 1339 or public health center first for medical consultation, and then visit a COVID-19 screening center in your area.<br>
※ 出现呼吸道症状或疑似感染新型冠状病毒肺炎时，请先向管辖区保健所或1339呼叫中心进行咨询后再前往指定诊疗机构.</font>







Statistics
============================

```{r}
library(plotly)
library(ggplot2)
library(tidyverse)
urlfile2= "https://raw.githubusercontent.com/Yunjeong-Kim/covid19_south_korea/master/daily_total.csv"
dat <- read_csv(url(urlfile2))
covid19 <- data.frame(t(dat[-1]))
colnames(covid19)[1:5] <- c("test", "negative", "confirmed", "released", "death")
covid19<-tibble::rownames_to_column(covid19, "date") 
covid19 <- covid19 %>%
  mutate(cumconfirmed = cumsum(confirmed)) %>%
  mutate(cumdeath = cumsum(death)) %>%
  mutate(cumreleased = cumsum(released)) %>%
  mutate(date = as.Date(date, format="%m/%d/%Y"))
urlfile3= "https://raw.githubusercontent.com/Yunjeong-Kim/covid19_south_korea/master/daily_province.csv"
caseProvince <- read_csv(url(urlfile3))
colnames(caseProvince)[1:1] <- c("date")
caseProvince <- caseProvince %>%
  mutate(cumSeoul = cumsum(Seoul)) %>%
  mutate(cumDaegu = cumsum(Daegu)) %>%
  mutate(cumGyeonggi = cumsum(Gyeonggido)) %>%
  mutate(cumGyeongbuk = cumsum(Gyeongsangbukdo)) %>%
  mutate(date = as.Date(date, format="%m/%d/%Y"))
urlfile4="https://raw.githubusercontent.com/Yunjeong-Kim/covid19_south_korea/master/daily_province_time_series.csv"
provinceMap <- read_csv(url(urlfile4))
total <- data.frame(rowSums(provinceMap[,-1:-3]))
sidoList <- data.frame(provinceMap[,1:3])
total <- cbind(total, sidoList)
newCol <- c("cumulative", "province", "lat", "lon")
colnames(total) <- newCol
  
```

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
confirmed <- as.numeric(apply(covid19[4], 2, sum))
death <- as.numeric(apply(covid19[6], 2, sum))
tested <- as.numeric(apply(covid19[2], 2, sum))
released <- as.numeric(apply(covid19[5], 2, sum))
city <- levels(as.factor(total$province))
inputPanel(
  h3('COVID-19 Status'),
  selectInput("city", label = "Select your city", choices = city, selected = "Daegu", width=180))
```

```{r}
output$confirmed <- renderPrint({confirmed})
output$death <- renderPrint({death})
output$deathrate <- renderPrint({death/confirmed})
output$tested <- renderPrint({tested})
output$released <- renderPrint({released})
```


##### Total Confirmed {.value-box}
```{r}
renderValueBox({
  valueBox(
    value = confirmed, 
    color = "#4682B4"
  )
})
```

##### Total Death {.value-box}
```{r}
renderValueBox({
  valueBox(
    value = death, 
    color = "#20B2AA"
  )
})
```

##### Total Tested {.value-box}
```{r}
renderValueBox({
  valueBox(
    value = tested, 
    color = "#20B2AA"
  )
})
```

##### Total Released {.value-box}
```{r}
renderValueBox({
  valueBox(
    value = released, 
    color = "#20B2AA"
  )
})
```
<br>
<font size="1"> Source:[Korea Centers for Disease and Prevention](http://www.cdc.go.kr/index.es?sid=a2)</font>



Column {data-width = 450}
-----------------------------------------------------------------------
### COVID-19 South Korea Map 

```{r}
library(leaflet)
total$province <- as.factor(total$province)
subDat <- reactive({
  total %>% 
    mutate(selected = 0)
  })
finalDat <- reactive({
  subDat() %>%
    mutate(selected = ifelse((length(input$city) > 0) & (province == noquote(input$city)), 1, 0))
})
pals <- colorFactor(c("#4169E1", "#DC143C"), domain = c(1, 0))
renderLeaflet({
  leaflet(finalDat()) %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addCircleMarkers(
      stroke = FALSE,
      lng = ~lon, lat = ~lat,
      label = ~cumulative, 
      radius = ~sqrt(cumulative),
      color = ~pals(selected),
      labelOptions = labelOptions(
        noHide = TRUE, 
        offset=c(0,-12),
        textOnly=TRUE, 
        style=list('color'='black', 'font-size'='15px')                                      ))
  
})
```


Column {data-width= 450}
-----------------------------------------------------------------------

### Daily Cases and Released

```{r}
colors1 <- c("Daily Confirmed" = "#FC4E07", "Daily Released" = "#4682B4")
plot1 <-ggplot(covid19, ) +
        #geom_bar(aes(x=date, y=confirmed, fill = "Daily Confirmed"), stat = "identity") + 
        geom_line(aes(x=date, y=confirmed, color = "Daily Confirmed"), stat="identity", size = 1.5) +
        geom_line(aes(x=date, y=released, color = "Daily Released"), stat="identity", size = 1.5) +
        labs(x="Date", y="Number", color="Legend") +
        scale_color_manual(values = colors1) +
        theme(axis.text.x=element_text(angle=45,hjust=1)) +
        theme_minimal()
plot1
ggplotly(plot1)
```

### Total Cases and Death

```{r}
colors2 <- c("Cumulative Confirmed" = "#4682B4", "Cumulative Death" = "#E7B800")
plot2 <-ggplot(covid19, ) +
        geom_line(aes(x=date, y=cumdeath, color = "Cumulative Death"), stat="identity", size = 1.5) +
        geom_line(aes(x=date, y=cumconfirmed, color = "Cumulative Confirmed"), stat="identity", size = 1.5) +
        labs(x="Date", y="Number", color="Legend") +
        scale_color_manual(values = colors2) +
        theme(axis.text.x=element_text(angle=45,hjust=1)) +
        theme_minimal()
plot2
ggplotly(plot2)
```

### Cases by City/Province

```{r}
colors3 <- c("Seoul"="steelblue", "Daegu"="#FC4E07", "Gyeonggi-do"="#00AFBB", "Gyeongsangbuk-do" = "#E7B800")
plot3 <- ggplot(caseProvince, ) +
  geom_line(aes(x=date, y=cumSeoul, color = "Seoul"), stat="identity", size = 1.5) +
  geom_line(aes(x=date, y=cumDaegu, color = "Daegu"), stat="identity", size = 1.5) +
  #geom_line(aes(x=date, y=cumGyeonggi, color = "Gyeonggi-do"), stat="identity", size = 1.5) +
  geom_line(aes(x=date, y=cumGyeongbuk, color = "Gyeongsangbuk-do"), stat="identity", size = 1.5) +
  labs(x="Date", y="Confirmed Cases", color="Legend") +
  scale_color_manual(values = colors3) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme_minimal()
plot3
ggplotly(plot3)
```


About
===================

<font size="2">The data and dashboard are refreshed on a daily basis.</font>


<font size="2">The raw data is pulled from [Korea Center for Disease Control and Prevention(KCDC)](https://www.cdc.go.kr/cdc_eng/) and [Ministry of Health and Welfare](https://www.mohw.go.kr/react/popup_200128_2.html?fbclid=IwAR0naRh5ksc0Vj7HUOboJmf1WLRx2EKV6YnNs_5ns4MJ6YQ2-JzyVwEHNA0).</font>

<br>

**COVID-19 in South Korea**

This app is for the COVID-19 in South Korea mapping project for "Data Science for Public Health 1" at Johns Hopkins Bloomberg School of Public Health. 

<br>

**COVID-19 South Korea App**

https://taeeun-kwon.shinyapps.io/covid19_SouthKorea/

We have two sections in our app. The first section is an interactive map which shows all COVID-19 testing centers in South Korea, and the second section is the statistics of cumulative, daily and released cases in South Korea from January to current time. 

<br>

**Data source**

1. Covid-19 Testing Center Map 
 We have two sections in our app. The first section is an interactive map which shows all testing centers in South Korea. The data were scrapped from Korean [Ministry of Health and Welfare](https://www.mohw.go.kr/react/popup_200128_2.html?fbclid=IwAR0naRh5ksc0Vj7HUOboJmf1WLRx2EKV6YnNs_5ns4MJ6YQ2-JzyVwEHNA0). We added the GPS data (latitude and longitude) of each testing center based on google map. We color-coded the testing centers according to COVID-19 testing availability and also included detailed information of each testing center. 

2. Statistics 
 The data were extracted from [DS4C (Data Science for COVID19)](https://github.com/jihoo-kim/Data-Science-for-COVID-19) and edited with additional data from [Korea Center for Disease Control and Prevention(KCDC)](https://www.cdc.go.kr/cdc_eng/).
  
<br> 
  
**Team Members and Role**

 * *Taeeun Kwon (Johns Hopkins Bloomberg School of Public Health)* : Collecting COVID-19 testing centers data, Designing and Coding for the interactive map of COVID-19 testing centers and overall dashboard.

 * *Shudi Pan (Johns Hopkins Bloomberg School of Public Health)* : Coding for the basic structure of the interactive map of COVID-19 testing centers as well as further improvements. 

 * *Yunjeong Kim (Johns Hopkins Bloomberg School of Public Health)* : Collecting COVID-19 case data, Designing the overall structure of the Statistic Page, Coding for visualization of COVID-19 statistics (including plotting and mapping) in the statistic page.

<br>

**Acknowledgements**

 Thanks sincerely to *JunYoung Kim (University of Nevada Las Vegas, DataX Lab)* for his contribution to data collection.

<br>

**Disclaimer**

 This is an assignment of Johns Hopkins Data Science for Public Health. 

<br>

**Contact**

 For any question or feedback, you can contact us (tkwon5@jh.edu). More information about this dashboard can be found in this [github](https://github.com/Yunjeong-Kim/covid19_south_korea).